Religion and Its Influence on Social Issues^[Code and data are available at: https://github.com/dudqo/religion_survey]

### 2022-04-27 outputs/paper/paper.Rmd
introduction

This research will focus on some social issues in the United States and how opinions of people of different religion differs.

>>>>

This research will focus on some social issues in the United States and how opinions of people of different religion differs. As the original dataset had very large amount data related to the topic of this research, decisions had to me made on which data to use. For the paper to be more effective on studying the influence of religion on social issues, data on popular social problems in modern society, especially in the United States have been chosen.
